Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-04-25 doc/paper.tex
updates results

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

@@

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                       & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                   \\
            \hline
            Scratch                    & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                  \\
            Supervised                 & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16) \\
            \hline
            PointContrast              & 91.97          & \textbf{96.67} & 82.4           & 0              & 17.84          & 56.49          & \textbf{75.39} & \textbf{77.63} & 87.35          & 63.3           & 73.53          & \textbf{79.55} & 58.76          & 66.22 (+1.16)          \\
            PointContrast - Same Scan  & 91.03          & 96.27          & \textbf{82.8}  & 0              & 31.53          & 57.27          & 69.33          & 76.97          & \textbf{88.83} & 45.49          & 71.02          & 77.09          & 57.06          & 64.97 (-0.09)          \\
            Contrastive Scene Contexts & \textbf{92.34} & 96.02          & 83.53          & 0              & \textbf{40.88} & \textbf{57.73} & 72.11          & 77.5           & 88.15          & \textbf{74.61} & \textbf{74.52} & 76.45          & \textbf{62.64} & \textbf{68.96} (+3.9)  \\
            CME \textbf{(Ours)}        & 90.8           & 96.57          & 82.52          & \textbf{0.110} & 30.94          & 56.94          & 68.71          & 75.12          & 88.48          & 71.7           & 72.17          & 73.783         & 56.35          & 66.48 (+1.42)          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5              \\
            \hline
            Scratch             & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                 \\
            Supervised          & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2) \\
            \hline
            PointContrast       & 0    & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 (+1.8)          \\
            CME \textbf{(Ours)} & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 (+2.8)          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

% \begin{table}[t!]
%     \centering

%     \begin{tabular}{ c | c c c c c c}
%                             & 5\%  & 10\% & 20\% & 30\% & 40\% & 100\% \\
%         \hline
%         Scratch             & 56.9 &      & 64.1 &      & 65.6 &       \\
%         \hline
%         PointContrast       &      &      &      &      &      &       \\
%         CME \textbf{(Ours)} & 60.8 &      & 64.8 &      & 64.7 &       \\
%     \end{tabular}

%     \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
%     \label{table:scannetVaryingDataAmount}
% \end{table}

\begin{table}[t!]
    \centering
    \resizebox{0.4\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                & 5\%   & 10\%  & 20\%  & 30\%  & 40\%  & 100\% \\
            \hline
            Scratch             & 42.2  & 51.09 & 58.23 & 59.23 & 62.17 & 67.43 \\
            \hline
            PointContrast       & 44.79 & 55.28 & 57.98 & 58.97 & 63.17 &       \\
            CME \textbf{(Ours)} & 44.04 & 51.19 & 57.3  & 60.73 & 63.31 & 67.71 \\
        \end{tabular}
    }
    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table}

>>>>

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{rotating}

@@

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                                   & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                   \\
            \hline
            Scratch                                & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                  \\
            Supervised                             & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16) \\
            \hline
            PointContrast                          & 91.97          & \textbf{96.67} & 82.4           & 0              & 17.84          & 56.49          & \textbf{75.39} & \textbf{77.63} & 87.35          & 63.3           & 73.53          & \textbf{79.55} & 58.76          & 66.22 (+1.16)          \\
            PointContrast - Same Scan              & 91.03          & 96.27          & \textbf{82.8}  & 0              & 31.53          & 57.27          & 69.33          & 76.97          & \textbf{88.83} & 45.49          & 71.02          & 77.09          & 57.06          & 64.97 (-0.09)          \\
            PointContrast - 70\% overlap           & 91.85          & 96.56          & 83.55          & 0              & 28.25          & 59.36          & 73.53          & 78.51          & 88.28          & 79.95          & 74.61          & 76             & 61.08          & 68.58 (+3.52)          \\
            Contrastive Scene Contexts             & \textbf{92.34} & 96.02          & 83.53          & 0              & \textbf{40.88} & \textbf{57.73} & 72.11          & 77.5           & 88.15          & \textbf{74.61} & \textbf{74.52} & 76.45          & \textbf{62.64} & \textbf{68.96} (+3.9)  \\
            Contrastive Scene Contexts - Same Scan & 91.68          & 96.59          & 83.21          & 0              & 40.38          & 58.12          & 70.42          & 76.77          & 87.13          & 69.33          & 68.77          & 82.34          & 58.45          & 67.94 (+2.88)          \\
            CME \textbf{(Ours)}                    & 90.8           & 96.57          & 82.52          & \textbf{0.110} & 30.94          & 56.94          & 68.71          & 75.12          & 88.48          & 71.7           & 72.17          & 73.783         & 56.35          & 66.48 (+1.42)          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                                   & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5              \\
            \hline
            Scratch                                & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                 \\
            Supervised                             & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2) \\
            \hline
            PointContrast                          & 0    & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 (+1.8)          \\
            PointContrast - Same Scan              & 0    & 19.8          & 70.7          & 92.1 & 48.4          & 90.5          & 81.8          & 38.4          & 90.4          & 34.1          & 56.6 (+3.6)          \\
            PointContrast - 70\% overlap           & 0    & 22.6          & 71.6          & 94.6 & 45.8          & 87.9          & 71.7          & 37.0          & 81.0          & 40.9          & 55.3 (+2.3)          \\
            Contrastive Scene Contexts             & 0    & 32.9          & 69.2          & 93.0 & 47.6          & 87.5          & 80.9          & 39.6          & 87.5          & 40.4          & 57.8 (+4.8)          \\
            Contrastive Scene Contexts - Same Scan & 0    & 32.0          & 69.3          & 96.1 & 38.7          & 89.4          & 87.6          & 38.8          & 81.3          & 38.8          & 57.2 (+4.2)          \\
            CME \textbf{(Ours)}                    & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 (+2.8)          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%                    & 10\%                   & 20\%                  & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                    & 42.2                   & 51.09                  & 58.23                 & 59.23                  & 62.17                  & 67.43                  \\
            \hline
            PointContrast              & 44.79 \textbf{(+2.59)} & 55.28 \textbf{(+4.19)} & 57.98 (-0.25)         & 58.97 (-0.26)          & 63.17 \textbf{(+1.00)} & 66.88 (-0.55)          \\
            Contrastive Scene Contexts & 42.6 \textbf{(+0.4)}   & 53.03 \textbf{(+1.94)} & 57.28 (-0.95)         & 62.15 \textbf{(+2.92)} & 65.15 \textbf{(+2.98)} & 67.62 \textbf{(+0.19)} \\
            CME \textbf{(Ours)}        & 44.04 \textbf{(+1.84)} & 52.97 \textbf{(+1.88)} & 58.6 \textbf{(+0.37)} & 60.73 \textbf{(+1.5)}  & 63.31 \textbf{(+1.14)} & 67.71 \textbf{(+0.28)} \\
        \end{tabular}
    }
    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}[b]{ c | l c c c c c c c c c c c c c c c c c | c }
                                       & \begin{turn}{-90}cabinet \end{turn} & \begin{turn}{-90} bed  \end{turn} & \begin{turn}{-90} chair \end{turn} & \begin{turn}{-90} sofa \end{turn} & \begin{turn}{-90} table \end{turn} & \begin{turn}{-90} door \end{turn} & \begin{turn}{-90}  window \end{turn} & \begin{turn}{-90} bookshelf \end{turn} & \begin{turn}{-90} picture \end{turn} & \begin{turn}{-90} counter \end{turn} & \begin{turn}{-90} desk \end{turn} & \begin{turn}{-90} curtain \end{turn} & \begin{turn}{-90} refrigerator \end{turn} & \begin{turn}{-90}  Shower curtain \end{turn} & \begin{turn}{-90}  toilet \end{turn} & \begin{turn}{-90} sink  \end{turn} & \begin{turn}{-90} bathtub  \end{turn} & \begin{turn}{-90} otherfurniture \end{turn} & mAP@0.5     \\

            scratch                    & 45.8                       & 72.7                       & 79.8                       & 60.6                       & 69.5                       & 37.8                       & 28.9                       & 44.2                       & 17.8                       & 16.6                       & 24.8                       & 24.0                       & 45.3                       & 63.4                       & 93.1                       & 46.6                       & 78.5                       & 33.4                       & 49.0        \\
            \hline
            PointContrast              & 45.6                       & 68.9                       & 76.0                       & 62.7                       & 65.2                       & 38.5                       & 33.2                       & 53.7                       & 15.9                       & 20.9                       & 31.6                       & 23.2                       & 36.6                       & 55.5                       & 1.0                        & 48.0                       & 76.9                       & 31.6                       & 49.1 (+0.1) \\
            Contrastive Scene Contexts & 48.6                       & 63.5                       & 79.0                       & 64.3                       & 65.0                       & 35.9                       & 32.8                       & 48.8                       & 15.0                       & 27.1                       & 38.3                       & 19.1                       & 44.9                       & 50.4                       & 94.6                       & 49.1                       & 76.3                       & 34.3                       & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        & 45.3                       & 72.8                       & 76.2                       & 66.2                       & 63.2                       & 38.2                       & 25.4                       & 49.7                       & 18.6                       & 21.0                       & 34.3                       & 20.2                       & 39.2                       & 58.9                       & 94.8                       & 45.0                       & 73.9                       & 30.0                       & 48.5 (-0.5) \\
            \hline
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation Results (mAP@0.5)}
    \label{table:scannetInstanceSegmention}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.6\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\% & 10\% & 20\% & 30\% & 40\% & 100\%       \\
            \hline
            Scratch                    &     &      &      &      &      & 49.0        \\
            \hline
            PointContrast              &     &      & 40.5 & 43.0 & 43.9 & 49.1 (+0.1) \\
            Contrastive Scene Contexts &     &      & 41.6 & 42.9 & 44.6 & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        &     &      & 39.1 & 42.4 & 43.6 & 48.5 (-0.5) \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                       & ceiling & floor & wall & beam & column & window & door & table & chair & sofa & bookcase & board & clutter & mIOU \\
            \hline
            Scratch                    &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
            \hline
            PointContrast              &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
            Contrastive Scene Contexts &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
            CME \textbf{(Ours)}        &         &       &      &      &        &        &      &       &       &      &          &       &         &      \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{c | c c c c}
                                       & Scannet & S3DIS & SunRGBD & semanticKITTI \\
            \hline
            Scratch                    & 35.2    &       & 32.0    &               \\
            \hline
            PointContrast              & 36.7    &       & 34.2    &               \\
            Contrastive Scene Contexts & 36.1    &       & 33.2    &               \\
            CME \textbf{(Ours)}        & 37.7    &       & 33.1    &               \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}
